### 2020-03-25 tex/abstract.tex
edit abstract

\begin{abstract}
This document introduces several aspects related to the confirm activity problem in 
the NuCypher KMS network. These include the current adopted solution, its relation 
with both the fees and the inflation rewards, and three potential solutions that can be 
used to provide a proof that an Ursula has served a specific number of re-encryption 
requests within a given a period. We argue that the latter is a better option to be used 
for computing the fees that Alice paid for an Ursula in the network, but not for 
computing the inflation rewards.
\end{abstract}

>>>>

\begin{abstract}
This document introduces several aspects related to the confirm activity problem in 
the NuCypher network. These include the different definitions of this problem, the 
underlying threat model, the current adopted solution, and its relation 
to both the fees and the inflation rewards. Then we present potential solutions 
for the two types of the confirm activity issue, namely, confirm availability 
and confirm service activity. The former confirms that Ursula is available all the time 
and replies to all requests coming from Bob, while the latter provides a proof that an 
Ursula has served a specific number of distinct re-encryption 
requests within a given a period. We discuss the different solutions and outline at 
what stage of the network operation they are likely to be used.
\end{abstract}
